Pillar 1 - Sequential Pattern Mining

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
changes repetition of str_remove to str_remove_all

  AR %>%
    as("data.frame") %>%
    filter(
      count >= 1
    ) %>%
    mutate(
      rules = str_remove(rules, pattern = "[{]"),
      rules = str_remove(rules, pattern = "[}]"),
      rules = str_remove(rules, pattern = "[{]"),
      rules = str_remove(rules, pattern = "[}]"), #this is needed 4 times, because it only removes the first instance
      `rhs.support` = confidence / lift
    ) %>%
    separate(rules, into = c("lhs", "rhs"), sep="=>") %>%
    mutate_at(
      c("support", "lhs.support", "confidence", "rhs.support", "lift"),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, count, lhs.support,
      confidence, rhs.support,
      lift
    ) %>%
    arrange(
      desc(count)
    )

@@

# Transform AR from apriori into a readable data frame
clean_rules <- function(rules){
  rules %>%
    as("data.frame") %>%
    # filter(
    #   count >= 1
    # ) %>%
    mutate(
      rule = str_remove(rule, pattern = "[<]"),
      rule = str_remove(rule, pattern = "[{]"),
      rule = str_remove(rule, pattern = "[}]"),
      rule = str_remove(rule, pattern = "[>]"),
      rule = str_remove(rule, pattern = "[<]"),
      rule = str_remove(rule, pattern = "[{]"),
      rule = str_remove(rule, pattern = "[}]"),  #this is repeated, because it only removes the first instance
     # rule = str_remove(rule, pattern = "[>]"), #this is taken out because the rules is marked with a => so it removes that one. 
      `rhs.support` = confidence / lift
    ) %>%
    separate(rule, into = c("lhs", "rhs"), sep="=>") %>%
    mutate(
      lhs = str_remove(rule, pattern = "[<]"),
      lhs = str_remove(rule, pattern = "[{]"),
      lhs = str_remove(rule, pattern = "[}]"),
      lhs = str_remove(rule, pattern = "[>]"),
      rhs = str_remove(rule, pattern = "[<]"),
      rhs = str_remove(rule, pattern = "[{]"),
      rhs = str_remove(rule, pattern = "[}]"),
      rhs = str_remove(rule, pattern = "[>]")
    ) %>%
    mutate_at(
      c("support", #"lhs.support",
        "confidence", "rhs.support", "lift"),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, #count, lhs.support,
      confidence, rhs.support,
      lift
    ) #%>%
    #arrange(
    #  desc(count)
    #)

>>>>

  AR %>%
    as("data.frame") %>%
    filter(
      count >= 1
    ) %>%
    mutate(
      rules = str_remove_all(rules, pattern = "[{]"),
      rules = str_remove_all(rules, pattern = "[}]"),
      # rules = str_remove(rules, pattern = "[{]"),
      # rules = str_remove(rules, pattern = "[}]"), #this is needed 4 times, because it only removes the first instance
      `rhs.support` = confidence / lift
    ) %>%
    separate(rules, into = c("lhs", "rhs"), sep="=>") %>%
    mutate_at(
      c("support", "lhs.support", "confidence", "rhs.support", "lift"),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, count, lhs.support,
      confidence, rhs.support,
      lift
    ) %>%
    arrange(
      desc(count)
    )

@@

# Transform AR from apriori into a readable data frame
clean_rules <- function(rules){
  rules %>%
    as("data.frame") %>%
    # filter(
    #   count >= 1
    # ) %>%
    mutate(`rhs.support` = confidence / lift) %>%
    separate(rule, into = c("lhs", "rhs"), sep="=>") %>%
    mutate(
      lhs = str_remove(lhs, pattern = "[<]"),
      lhs = str_remove(lhs, pattern = "[{]"),
      lhs = str_remove(lhs, pattern = "[}]"),
      lhs = str_remove(lhs, pattern = "[>]"),
      rhs = str_remove(rhs, pattern = "[<]"),
      rhs = str_remove(rhs, pattern = "[{]"),
      rhs = str_remove(rhs, pattern = "[}]"),
      rhs = str_remove(rhs, pattern = "[>]")
    ) %>%
    mutate_at(
      c("support", #"lhs.support",
        "confidence", "rhs.support", "lift"),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, #count, lhs.support,
      confidence, rhs.support,
      lift
    ) #%>%
    #arrange(
    #  desc(count)
    #)
